---
title: "eds212_day2_activities"
author: "Jared Petry"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("palmerpenguins")
library(palmerpenguins)
library(tidyverse)
```


GitHub reminder! do this in the console not here
```{r}
#----tell git to make a repository for this
#usethis::use_git()
#usethis::use_github
```

Derive f(x)=x^2 and evaluate slope at x=3
```{r}
func1 <- expression(x^2)
my_deriv <- D(func1, "x")
my_deriv
x <- 3
eval(my_deriv)
```

Now derive P(a)=2(3a+2)^4−5 and find slope at a=1.2
```{r}
func2 <- expression(2*(3*a+2)^4 - 5)
my_deriv2 <- D(func2, "a")
a <- 1.2
eval(my_deriv2)
```

Same thing with g(t)
```{r}
func3 <- expression((-4*t)/((t^2 +1)^3))
my_deriv3 <- D(func3 , "t")
t <- 0
eval(func3)
```


Make a penguin plot bill length vs. bill depth 
```{r}
ggplot(data=penguins, aes(x=bill_depth_mm, y=bill_length_mm )) +
  geom_point(aes(color=species))
```

```{r}
ggplot(data=penguins, aes(x=species, y=flipper_length_mm))+
  geom_jitter()+
  labs(x="species", y="flipper length", title= "Flipper Length by Species")
```

ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = species), size=1) +
  facet_wrap(~island) +
  theme_minimal() +
  labs(x="Body Mass (g)", y="Flipper Length (mm)", title = "Cute Fluffy Penguins")
  
```{r}

```

